%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[american]{babel}
\usepackage[margin=1in]{geometry}
\usepackage[sfdefault,light]{inter}
\usepackage{microtype}
\usepackage{enumitem}

\begin{document}
\pagestyle{empty}

\section*{Festival Zero \hrulefill}
\subsection*{Measuring impact on people and places}

Festival Zero has been running in Holyrood Park, Edinburgh, for two years. In preparation for its third edition, the organizers aim to better understand the festival's impact on the city from a social and economic perspective. The goal of this challenge is to collect data that capture Festival Zero's impact on hospitality, other cultural venues, and the environment, and build an evidence-based narrative to attract sponsors and donors.
\paragraph{Available data} Event financial metrics, attendance figures, social media metrics

\vfill

\section*{StART-up \hrulefill}
\subsection*{From creative ideas to sustainable creativity}

StART-up is a new cultural organization that runs small-scale events in a building formerly owned by the University of Edinburgh. While it has very clear cultural and artistic objectives, it lacks a thorough undertanding of the sustainability of its activities, especially in financial terms. The goal of this challenge is to develop the organization's strategic goals and figure out how to remain economically viable in the medium and long term.
\paragraph{Available data} Mission statement, three-year financial forecasts

\vfill

\section*{This Is Contemporary \hrulefill}
\subsection*{Responding to crisis through community engagement}

This Is Contemporary is an art gallery based in Leith. Given recent cuts to public funding, the gallery must find new ways to secure financial resources needed to create cultural value. It believes these could come from a more connected and vibrant community that engages with the gallery online and in person. The goal of this challenge is to review community engagement initiatives by other cultural organizations and evaluate their potential.
\paragraph{Available data} Strategic plan, financial statements, portfolio, social media metrics

\vfill

\section*{You! Yes, You! \hrulefill}
\subsection*{Equity, diversity, and inclusion in the arts}

You! Yes, You! is a well-established cultural organization in Glasgow whose multifunctional space hosts a variety of events, such as exhibitions, performances, concerts, workshops, and talks. It is currently exploring options to increase equity, diversity, and inclusion (EDI) activities in order to broaden its cultural and social impact. The goal of this challenge is to benchmark EDI practices among similar organizations and come up with a strategy.
\paragraph{Available data} Strategic plan, financial statements, current activities

\end{document}
